---
title: "An introduction to reproducible research practices for social scientists"
author: "Jenine K. Harris"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  word_document: 
    reference_docx: "template.docx"
  bookdown::word_document2: 
    reference_docx: "template.docx"
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
editor_options: 
  markdown: 
    wrap: 72
---

# Chapter 1: Science vs. Memes (\#chapter1)

> "I don't know if Franklin actually said this but I like it anyway!" -
> Uncle Nick, Facebook, August 30, 2016

In the months just prior to the 2016 Presidential election, the
political differences between me and some of my family members became
very clear. One place this showed up was on Facebook, where I would use
Fact Checking websites like Snopes to challenge or debunk memes often
showing false quote or facts posted by my Uncle Nick. This frequent
interaction culminated in Nick adding a disclaimer (quoted above) to a
meme he shared on Facebook. The meme included a picture of Benjamin
Franklin with the quote, "Make yourself sheep and the wolves will eat
you" attributed to Franklin and a logo for The Patriot Post. This quote
is accurately attributed to Benjamin Franklin, but this was not
important to Nick. The important part was that he liked the quote and
wanted to share it with others. Nick is not the only one using social
media to share information, nor is social media the only place where
information is shared.

In everyday life we are surrounded by sources of information. We have
online and offline conversations with friends and colleagues and Uncle
Nick, read comments from strangers on the internet, watch news online
and on television, and read magazines and books and government reports.
Maybe we even look up and read (or skim) the occasional scientific
article. Not all of these sources of information are the same. Sources
of information vary widely in quality.

There are many different things that can impact the quality of
information. Information quality can be impacted by the author of the
information through author bias, author motive, and author expertise.
Information quality can also be impacted by the .

Author bias

Author motive

Author expertise

## The scientific quality crisis 

The impact on human health 

ii. Reasons for poor quality 
1. Fraud (26%) 
2. Error (74%)  

## How reproducible research can help 

i. Increases research quality, promotes collaboration, reduces research waste 
ii. Distinction from repeatable and replicable iii. 

## Qualities that make research reproducible 

1. Access to data and software 

2. Well-organized statistical code or sufficiently detailed methods

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-methods-sections.Rmd-->

# Literature

Here is a review of existing methods.

<!--chapter:end:02-statistical-code.Rmd-->

# Methods

We describe our methods in this chapter.

Math can be added in body using usual syntax like this 

## math example

$p$ is unknown but expected to be around 1/3. Standard error will be approximated

$$
SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
$$

You can also use math in footnotes like this^[where we mention $p = \frac{a}{b}$].

We will approximate standard error to 0.027[^longnote]

[^longnote]: $p$ is unknown but expected to be around 1/3. Standard error will be approximated

    $$
    SE = \sqrt(\frac{p(1-p)}{n}) \approx \sqrt{\frac{1/3 (1 - 1/3)} {300}} = 0.027
    $$

<!--chapter:end:03-documenting-data.Rmd-->

# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

## Example two

<!--chapter:end:04-sharing-code-data.Rmd-->

# Final Words

We have finished a nice book.

<!--chapter:end:05-strategies-private-data.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-conclusion.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:07-references.Rmd-->

